A multiverse analysis of the associations between internet use and well-being

### 2023-11-13 ms.Rmd
Improve reproducibility
Sample specs for synthetic data

Require Hmisc

More reproducibility improvements

More reproducibility

library(papaja)
library(scales)
library(knitr)
library(lme4)
library(ggh4x)
library(emmeans)
library(ggside)
library(Hmisc)
library(ggbeeswarm)
library(broom.mixed)
library(patchwork)
library(ggdist)
library(corrr)
library(tidyverse)
opts_chunk$set(
  include = FALSE,
  cache = TRUE
)

@@

# If only simulated data exists, run just 1 spec by every X, Y pair
set.seed(9091090)
if (DATA_PATH_GWP == "") specs <- slice_sample(specs, n = 1, by = c(y, x))
```

@@

```{r}
#| label: fig-rq1
#| include: true
#| out.width: "\\textwidth"
#| fig.env: "figure*"
#| fig.height: 5.6
#| fig.width: 9
#| fig.cap: "Scatterplots of countries' mean well-being outcomes for individuals who responded No and Yes to the internet question, and their differences. Small points are countries' means, and solid colored points and lines are means of the countries' means. Numbers in each panel's left bottom corner indicate the regression coefficient (Yes - No) and its 95\% confidence interval. The GWBI outcomes did not overlap in time with mobile internet data."

>>>>

library(papaja)
library(scales)
library(knitr)
library(lme4)
library(ggh4x)
library(emmeans)
library(ggside)
library(Hmisc)
library(ggbeeswarm)
library(broom.mixed)
library(patchwork)
library(ggdist)
library(corrr)
library(tidyverse)
opts_chunk$set(
  include = FALSE,
  cache = TRUE,
  warning = FALSE
)

@@

# If only simulated data exists, run just 1 spec by every X, Y pair
set.seed(9091090)
if (DATA_PATH_GWP == "") specs <- slice_sample(specs, n = 2, by = c(y, x))
```

@@

```{r}
#| label: fig-rq1
#| include: true
#| out.width: "\\textwidth"
#| fig.env: "figure*"
#| fig.height: 5.6
#| fig.width: 9
#| fig.cap: "Scatterplots of countries' mean well-being outcomes for individuals who responded No and Yes to the internet question, and their differences. Small points are countries' means, and solid colored points and lines are means of the countries' means. Numbers in each panel's left bottom corner indicate the regression coefficient (Yes - No) and its 95\\% confidence interval. The GWBI outcomes did not overlap in time with mobile internet data."
